\documentclass[11pt,a4paper,sans]{moderncv}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}
\moderncvicons{letters} % FIX: Use letters (T, M, E) instead of icons to avoid missing fontawesome font
\renewcommand{\labelitemi}{\textbullet} % WORKAROUND: Use standard bullet to avoid missing fontawesome font

% adjust the page margins
\usepackage[scale=0.75]{geometry}
\usepackage{lmodern} % FIX: Use scalable fonts to avoid microtype expansion errors

% personal data
\name{Bach Chi}{Le}
\title{Applied Mathematics PhD Candidate} % Inferred title
\address{Bethlehem, PA, 18015}{}{}
\phone[mobile]{(484) 966-1766}
\email{lechibachh@gmail.com}
% \homepage{www.johndoe.com}
% \social[linkedin]{john.doe}

\begin{document}
\makecvtitle

\section{Education}
\cventry{Aug 2023--May 2025}{Master of Science in Financial Engineering}{Lehigh University}{Bethlehem, PA}{\textit{GPA: 3.93/4.0}}{}
\cventry{Aug 2020--Jul 2023}{Bachelor of Commerce in Finance and Economics}{University of Melbourne}{Melbourne, AU}{\textit{H1 -- First Class Honors}}{}

\section{Research Interests}
\cvitem{}{Financial Engineering, Optimization, Time Series Forecasting, Deep Learning, Robustness, Machine Learning in Finance}

\section{Awards and Honors}
\cvitem{2024}{Graduate Business Life Leadership Award, Lehigh University}
\cvitem{2024}{Center for Financial Services Research Fellowship, Lehigh University}
\cvitem{2023}{Director’s Scholarship, Lehigh University}
\cvitem{2022}{Melbourne International Undergraduate Scholarship, University of Melbourne}
\cvitem{2020}{Bachelor of Commerce Global Scholarship, University of Melbourne}

\section{Publications}
\subsection{Preprints}
\cvitem{2025}{Le, B. C., Dao, T. V., Nguyen, B. T., \& Chu, H. T. M. \textit{Tight Robustness Certificates and Wasserstein Distributional Attacks for Deep Neural Networks}. arXiv preprint arXiv:2510.10000.}

\subsection{Working Papers}
\cvitem{}{Moore, O. A., Mchiri, A., Grady-Moreno, A., \& Le, B. C. \textit{Identified but Dissatisfied: The Paradoxical Effects of Mixed Team Membership Configurations}. Manuscript in preparation.}
\cvitem{}{Moore, O. A., Gibson, H. O., Henderson, S. J., \& Le, B. C. \textit{Modeling the Effects of Multiple Team Membership on Project Delay: The Role of Expertise Diversity and HR Policy}. Manuscript in preparation.}

\subsection{Research in Progress}
\cvitem{}{Chu, H. T. M., Nguyen, B. T., \& Le, B. C. \textit{Wasserstein Distributional Robustness in Deep Learning: Lipschitz-Based Guarantees for Transformers}.}
\cvitem{}{Le, B. C., \& Nguyen, L. M. \textit{Ensemble Modeling for Time Series Forecasting via Adaptive Distributionally Robust Optimization}.}
\cvitem{}{Lamadrid, A. J., \& Le, B. C. \textit{Risk Management in Deregulated Commodity Markets: A Comparative Study of Stochastic, Robust, and Info-Gap Optimization Frameworks}.}
\cvitem{}{Tang, S., \& Le, B. C. \textit{On the Optimality of Balanced Pemantle’s Min-Plus Binary Trees: A Probabilistic and Inductive Approach}.}

\subsection{Presentations}
\cvitem{Jan 2025}{Moore, O. A., Mchiri, A., Grady-Moreno, A., \& Le, B. C. \textit{Mixed versus Traditional Multiple Team Membership Configurations: Understanding Team Satisfaction through the Mediating Role of Identity and Moderating Effect of Intra-Team Conflict}. Presented at the INGRoup 2025 Midyear Conference, Virtual.}

\section{Research Experience}
\cventry{June 2025--Present}{Research Assistant}{VinUniversity}{Hanoi, VN}{}{PI: Prof. Hong T. M. Chu
\begin{itemize}
\item Conduct comprehensive literature research and summarize relevant findings to support the research objectives, maintain an organized database of literature and references.
\item Conduct advanced academic research and scientific computations with a focus on sensitivity analysis, designing algorithms and stabilizing networks.
\item Assist teaching optimization topics in undergraduate course.
\end{itemize}}

\cventry{Sep 2024--May 2025}{Research Assistant}{Lehigh University, Industrial and Systems Engineering}{Bethlehem, PA}{}{PI: Prof. Lam M. Nguyen
\begin{itemize}
\item Develop an innovative Ensemble Modeling for Time Series Forecasting using the Adaptive Distributionally Robust Optimization (ADRO) framework.
\item Conduct extensive theoretical formulation and empirical testing to establish the effectiveness of the ADRO framework.
\item Provide mathematical proofs to derive a tractable robust counterpart for the original ADRO formulation.
\end{itemize}}

\cventry{Apr 2024--May 2025}{Research Assistant}{Lehigh University, Economics Department}{Bethlehem, PA}{}{PI: Prof. Alberto J. Lamadrid
\begin{itemize}
\item Conduct research on risk management strategies in deregulated commodity markets.
\item Implement advanced optimization models, including Stochastic Optimization, Robust Optimization, and Info-Gap Decision Theory frameworks.
\item Perform mathematical and numerical analysis to compare the effectiveness of different models.
\end{itemize}}

\cventry{Jan 2024--May 2025}{Research Assistant}{Lehigh University, Mathematics Department}{Bethlehem, PA}{}{PI: Prof. Si Tang
\begin{itemize}
\item Investigate the optimality of balanced Pemantle’s Min-Plus binary trees.
\item Employ R to compute probability density functions and expected values.
\item Develop induction hypotheses from computational insights.
\end{itemize}}

\cventry{Nov 2023--May 2025}{Research Assistant}{Lehigh University, Management Department}{Bethlehem, PA}{}{PI: Prof. Ozias A. Moore
\begin{itemize}
\item Engineer datasets by embedding Level 2 variables into a Level 1 dataset using Group Mean Centering and Grand Mean Centering techniques.
\item Conduct Monte Carlo simulations to bootstrap data and assess mediation effects.
\item Support research on Team Configuration (Multiple Team Membership) using Andrew Hayes’ PROCESS Model 7.
\end{itemize}}

\section{Professional Experience}
\cventry{Jun 2024--Aug 2024}{Complex Securities \& Financial Instruments Intern}{Stout Risius Ross}{New York, NY}{}{
\begin{itemize}
\item Applied option pricing models and conducted Monte Carlo simulations to accurately value complex derivatives.
\item Conducted real options analysis to assess the value of investments in commodities and low-stage companies.
\item Performed portfolio valuations and credit rating regressions using Excel, VBA, and R.
\end{itemize}}

\cventry{May 2024--Apr 2025}{Mathematics Consultant}{Outlier AI}{San Francisco, CA}{}{
\begin{itemize}
\item Create and refine training prompts and solutions across diverse mathematical fields to train Large Language Models (LLMs).
\item Formulate innovative mathematical problems and engage in rigorous math-focused conversations.
\item Evaluate and rate AI-generated responses to mathematical prompts based on rigorous standards.
\end{itemize}}

\cventry{Apr 2023--Apr 2024}{Research Consultant}{WorldQuant}{Hanoi, VN}{}{
\begin{itemize}
\item Developed and optimized alpha strategies for USA and China markets using technical indicators.
\item Conducted extensive backtesting over a 10-year period to validate performance.
\end{itemize}}

\section{Technical Skills}
\cvitem{Programming}{Python, R, SPSS, Latex, Pine Script, Excel VBA, SQL, C++, AMPL, MATLAB, Gurobi}
\cvitem{Software}{SAS, Stata, VS Code, PyCharm, RStudio, MySQL, Microsoft Office, GitHub, QuantConnect}

\end{document}
